---
title: "2019-02-03_Campbell_26"
author: "Nicolas May"
date: "2/11/2019"
output: 
  html_document:
    theme: sandstone
    highlight: zenburn
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load Requirements

### Load libraries

```{r}
library(dplyr)
library(stringr)
```

### Load useful constants / functions

```{r}
source("~/Desktop/config.R")
rm(BOX_CLIENT_ID); rm(BOX_CLIENT_SECRET); rm(BOX_REDIRECT_URI)
source("~/Desktop/helpers.R")

GET_API_DATA <- TRUE
```


## Get Data

### Define data fields & forms

#### UDS 3

```{r}
## FIELDS

# header
fields_u3_raw_vst <-
  c(
    "ptid"
    , "form_date"
  )
# ivp_c2
fields_u3_raw_c2 <-
  c(
    "mocatots"
    , "trailb_c2"
    , "trailbrr_c2"
    , "trailbli_c2"
    , "trailb_c2z"
  )
# ivp_d1
fields_u3_raw_d1 <-
  c(
    "normcog"    # NL
    , "mciamem"  # MCI
    , "mciaplus" # MCI
    , "mcinon1"  # MCI
    , "mcinon2"  # MCI
    , "impnomci" # Impaired not MCI
    , "alzdis"   # AD etio
    , "alzdisif"
    , "lbdis"    # LBD etio
    , "lbdif"
    , "msa"      # MSA etio
    , "msaif"
    , "psp"      # PSP etio
    , "pspif"
    , "ftldmo"   # FTLD motor etio
    , "ftldmoif"
    , "ftldnos"  # FTLD NOS etio
    , "ftldnoif"
  )

# combine header & Form C2 fields, prefixing C2 with "fu_" and "tele_"
fields_u3_raw <-
  c(
    fields_u3_raw_vst,
    fields_u3_raw_c2,
    paste0("fu_", fields_u3_raw_c2),
    paste0("tele_", fields_u3_raw_c2),
    fields_u3_raw_d1,
    paste0("fu_", fields_u3_raw_d1),
    paste0("tele_", fields_u3_raw_d1)
  )

fields_u3 <- fields_u3_raw %>% paste(collapse = ",")


## FORMS

forms_u3_raw <- 
  c(
    # Lichtenberg Financial Decision Making Screening Scale
    "lfdss_for_professionals"
  )

forms_u3 <- forms_u3_raw %>% paste(collapse = ",")
```

#### MiNDSet Registry

```{r}
fields_ms_raw <-
  c(
    "subject_id"
    , "exam_date"
    , "birth_date"
    , "race_value" # 1 Wht, 2 Blk, 3 Asn, 4 Hsp, 5 Oth, 6 Unk
    , "sex_value"  # 1 M, 2 F
    , "ed_level"   
    , "marital_status" # 1 Mrd, 2 Wdw, 3 Dvc, 4 Sep, 5 Nvr, 6 Sng, 7 Oth
  )

fields_ms <- fields_ms_raw %>% paste(collapse = ",")
```

### Retrieve data via REDCap API

#### UDS 3

```{r}
if (GET_API_DATA) {
  json_u3 <- rc_api_get(uri =    REDCAP_API_URI,
                        token =  REDCAP_API_TOKEN_UDS3n,
                        fields = fields_u3,
                        forms  = forms_u3)
}

df_u3 <- jsonlite::fromJSON(json_u3) %>% na_if("")
```

#### MiNDSet Registry

```{r}
if (GET_API_DATA) {
  json_ms <- rc_api_get(uri =    REDCAP_API_URI,
                        token =  REDCAP_API_TOKEN_MINDSET,
                        fields = fields_ms)
}

df_ms <- jsonlite::fromJSON(json_ms) %>% na_if("")
```

### Write raw data to csv

```{r}
data.table::fwrite(df_u3, "df_u3.csv", na = "")
data.table::fwrite(df_ms, "df_ms.csv", na = "")
```


## Process Data

### Clean data

#### UDS 3

Clean out DDE entry records (`--1`, `--2`).
```{r}
df_u3_cln <- df_u3 %>% 
  filter(str_detect(ptid, "^UM\\d{8}$"))
```

Clean out records with missing `form_date`s.
```{r}
df_u3_cln <- df_u3_cln %>% 
  filter(!is.na(form_date))
```

#### MiNDSet Registry

Get only UMMAP IDs.
```{r}
df_ms_cln <- df_ms %>% 
  filter(str_detect(subject_id, "^UM\\d{8}$"))
```

Clean out records with missing `exam_date`s.
```{r}
df_ms_cln <- df_ms_cln %>% 
  filter(!is.na(exam_date))
```

### Mutate data

#### UDS 3

Collapse initial visit / follow-up visit / telephone visit fields.
```{r}
df_u3_cln_mut <- collapse_ift_cols(df_u3_cln)
```

Guess data types.
```{r}
df_u3_cln_mut <- suppressMessages( readr::type_convert(df_u3_cln_mut) )
df_u3_cln_mut_cls_lis <- purrr::map(df_u3_cln_mut, class)
```

Simplify diagnosis and etiology fields.
```{r}
df_u3_cln_mut <- df_u3_cln_mut %>% 
  mutate(uds_dx_der = case_when(
    ftldnos  == 1 & ftldnoif == 1 ~ "FTLD",
    ftldmo   == 1 & ftldmoif == 1 ~ "FTLD",
    psp      == 1 & pspif    == 1 ~ "PSP",
    msa      == 1 & msaif    == 1 ~ "MSA",
    lbdis    == 1 & lbdif    == 1 ~ "LBD",
    alzdis   == 1 & alzdisif == 1 ~ "AD",
    impnomci == 1 ~ "Impaired no MCI",
    mcinon2  == 1 ~ "MCI",
    mcinon1  == 1 ~ "MCI",
    mciaplus == 1 ~ "MCI",
    mciamem  == 1 ~ "MCI",
    normcog  == 1 ~ "NL",
    TRUE ~ NA_character_
  ))
```

Generate visit numbers.
```{r}
df_u3_cln_mut <- calculate_visit_num(df_u3_cln_mut,
                                     id = ptid,
                                     date_field = form_date)
```

#### MiNDSet Registry

Coerce data types.
```{r}
# purrr::map(df_ms_cln, class)
df_ms_cln_mut <- df_ms_cln %>% 
  mutate(race_value = as.integer(race_value),
         sex_value  = as.integer(sex_value),
         ed_level   = as.integer(ed_level),
         marital_status = as.integer(marital_status),
         exam_date  = as.Date(exam_date),
         birth_date = as.Date(birth_date))
# purrr::map(df_ms_cln_mut, class)
```

Add age.
```{r}
df_ms_cln_mut <- calculate_age(df_ms_cln_mut,
                               birth_date = birth_date,
                               age_date = exam_date)
```


### Filter data

#### UDS 3

Get only most recent visits.
```{r}
df_u3_cln_mut_flt <- get_visit_n(df_u3_cln_mut,
                                 id_field = ptid,
                                 date_field = form_date,
                                 n = -Inf) # -Inf => earliest visit
```


## Join Data

### Left join: UDS 3 + MiNDSet Registry

Get rid of `redcap_event_name` fields.
```{r}
df_u3_cln_mut_flt <- df_u3_cln_mut_flt %>% 
  select(-redcap_event_name)
df_ms_cln_mut <- df_ms_cln_mut %>% 
  select(-redcap_event_name)
```

Perform left outer join.
```{r}
df_u3_ms <-
  FuzzyDateJoin::outer_left(x = df_u3_cln_mut_flt,
                            y = df_ms_cln_mut,
                            x_id_col = "ptid", y_id_col = "subject_id",
                            x_date_col = "form_date", y_date_col = "exam_date",
                            x_intvl_less = 120L, x_intvl_more = 120L,
                            keep_y_id = TRUE)
```

Reorder fields.
```{r}
# names(df_u3_ms)
df_u3_ms <- df_u3_ms %>%
  dplyr::select(
    -birth_date,
    -normcog, 
    -mciamem, -mciaplus,
    -mcinon1, -mcinon2,
    -impnomci,
    -alzdis, -alzdisif,
    -lbdis, -lbdif,
    -msa, -msaif,
    -psp, -pspif,
    -ftldmo, -ftldmoif,
    -ftldnos, -ftldnoif
  ) %>% 
  dplyr::select(ptid, form_date, visit_num, 
                uds_dx_der, uds_dx_date = exam_date,
                age_years, age_exact, age_units,
                race_value, sex_value, ed_level, marital_status,
                everything())
```


## Write Data

```{r}
readr::write_csv(df_u3_ms, "df_u3_ms.csv", na = "")
```


## Build Data Dictionaries

### UDS 3
```{r}
names_df_u3_ms <- names(df_u3_ms)
names_df_u3_ms <- str_replace_all(names_df_u3_ms, "___\\d{1,2}$", "")

json_data_dict_u3 <- RCurl::postForm(
  uri          = REDCAP_API_URI,
  token        = REDCAP_API_TOKEN_UDS3n,
  content      = 'metadata',
  format       = 'json',
  returnFormat = 'json'
)
df_data_dict_u3 <- jsonlite::fromJSON(json_data_dict_u3)

df_data_dict_u3_flt <- df_data_dict_u3 %>% 
  filter(field_name %in% names_df_u3_ms)
```

### MiNDSet Registry
```{r}
# names_df_u3_ms <- names(df_u3_ms)

json_data_dict_ms <- RCurl::postForm(
  uri          = REDCAP_API_URI,
  token        = REDCAP_API_TOKEN_MINDSET,
  content      = 'metadata',
  format       = 'json',
  returnFormat = 'json'
)
df_data_dict_ms <- jsonlite::fromJSON(json_data_dict_ms)

df_data_dict_ms_flt <- df_data_dict_ms %>% 
  filter(field_name %in% names_df_u3_ms)
```

## Write Data Dictionaries

```{r}
readr::write_csv(df_data_dict_u3_flt, "DataDictionary_UDS3.csv", na = "")
readr::write_csv(df_data_dict_ms_flt, "DataDictionary_MiNDSet.csv", na = "")
```






