---
title: "2019-02-03_Campbell_26"
author: "Nicolas May"
date: "2/11/2019"
output: 
  html_document:
    theme: sandstone
    highlight: zenburn
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load Requirements

### Load libraries

```{r}
library(dplyr)
library(stringr)
```

### Load useful constants / functions

```{r}
source("~/Desktop/config.R")
rm(BOX_CLIENT_ID); rm(BOX_CLIENT_SECRET); rm(BOX_REDIRECT_URI)
source("~/Desktop/helpers.R")

GET_API_DATA <- TRUE
```


## Get Data

### Define data fields & forms

#### UDS 3

```{r}
## FIELDS

# header
fields_u3_raw_vst <-
  c(
    "ptid"
    , "form_date"
  )
# ivp_c2
fields_u3_raw_c2 <-
  c(
    "mocatots"
    , "trailb_c2"
    , "trailbrr_c2"
    , "trailbli_c2"
    , "trailb_c2z"
  )
# ivp_d1
fields_u3_raw_d1 <-
  c(
    "normcog"    # NL
    , "mciamem"  # MCI
    , "mciaplus" # MCI
    , "mcinon1"  # MCI
    , "mcinon2"  # MCI
    , "impnomci" # Impaired not MCI
    , "alzdis"   # AD etio
    , "alzdisif"
    , "lbdis"    # LBD etio
    , "lbdif"
    , "msa"      # MSA etio
    , "msaif"
    , "psp"      # PSP etio
    , "pspif"
    , "ftldmo"   # FTLD motor etio
    , "ftldmoif"
    , "ftldnos"  # FTLD NOS etio
    , "ftldnoif"
  )

# combine header & Form C2 fields, prefixing C2 with "fu_" and "tele_"
fields_u3_raw <-
  c(
    fields_u3_raw_vst,
    fields_u3_raw_c2,
    paste0("fu_", fields_u3_raw_c2),
    paste0("tele_", fields_u3_raw_c2),
    fields_u3_raw_d1,
    paste0("fu_", fields_u3_raw_d1),
    paste0("tele_", fields_u3_raw_d1)
  )

fields_u3 <- fields_u3_raw %>% paste(collapse = ",")


## FORMS

forms_u3_raw <- 
  c(
    # Lichtenberg Financial Decision Making Self Efficacy Form
    "financial_decision_making_self_efficacy_form"
    # Lichtenberg Financial Decision Making Screening Scale
    , "lfdss_for_professionals"
  )

forms_u3 <- forms_u3_raw %>% paste(collapse = ",")
```

#### MiNDSet Registry

```{r}
fields_ms_raw <-
  c(
    "subject_id"
    , "exam_date"
    , "birth_date"
    , "race_value" # 1 Wht, 2 Blk, 3 Asn, 4 Hsp, 5 Oth, 6 Unk
    , "sex_value"  # 1 M, 2 F
    , "ed_level"   
    , "marital_status" # 1 Mrd, 2 Wdw, 3 Dvc, 4 Sep, 5 Nvr, 6 Sng, 7 Oth
  )

fields_ms <- fields_ms_raw %>% paste(collapse = ",")
```

### Retrieve data via REDCap API

#### UDS 3

```{r}
if (GET_API_DATA) {
  json_u3 <- rc_api_get(uri =    REDCAP_API_URI,
                        token =  REDCAP_API_TOKEN_UDS3n,
                        fields = fields_u3,
                        forms  = forms_u3)
}

df_u3 <- jsonlite::fromJSON(json_u3) %>% na_if("")
```

#### MiNDSet Registry

```{r}
if (GET_API_DATA) {
  json_ms <- rc_api_get(uri =    REDCAP_API_URI,
                        token =  REDCAP_API_TOKEN_MINDSET,
                        fields = fields_ms)
}

df_ms <- jsonlite::fromJSON(json_ms) %>% na_if("")
```

### Write raw data to csv

```{r}
data.table::fwrite(df_u3, "df_u3.csv", na = "")
data.table::fwrite(df_ms, "df_ms.csv", na = "")
```


## Process Data

### Clean data

#### UDS 3

Clean out DDE entry records (`--1`, `--2`).
```{r}
df_u3_cln <- df_u3 %>% 
  filter(str_detect(ptid, "^UM\\d{8}$"))
```

Clean out records with missing `form_date`s.
```{r}
df_u3_cln <- df_u3_cln %>% 
  filter(!is.na(form_date))
```

#### MiNDSet Registry

Get only UMMAP IDs.
```{r}
df_ms_cln <- df_ms %>% 
  filter(str_detect(subject_id, "^UM\\d{8}$"))
```

Clean out records with missing `exam_date`s.
```{r}
df_ms_cln <- df_ms_cln %>% 
  filter(!is.na(exam_date))
```

### Mutate data

#### UDS 3

Coalesce initial visit / follow-up visit / telephone visit fields.
```{r}
df_u3_cln_mut <- coalesce_ift_cols(df_u3_cln)
```

Guess data types.
```{r}
df_u3_cln_mut <- suppressMessages( readr::type_convert(df_u3_cln_mut) )
df_u3_cln_mut_cls_lis <- purrr::map(df_u3_cln_mut, class)
```

Simplify diagnosis and etiology fields.
```{r}
df_u3_cln_mut <- df_u3_cln_mut %>% 
  mutate(uds_dx_der = case_when(
    ftldnos  == 1 & ftldnoif == 1 ~ "FTLD",
    ftldmo   == 1 & ftldmoif == 1 ~ "FTLD",
    psp      == 1 & pspif    == 1 ~ "PSP",
    msa      == 1 & msaif    == 1 ~ "MSA",
    lbdis    == 1 & lbdif    == 1 ~ "LBD",
    alzdis   == 1 & alzdisif == 1 ~ "AD",
    impnomci == 1 ~ "Impaired no MCI",
    mcinon2  == 1 ~ "MCI",
    mcinon1  == 1 ~ "MCI",
    mciaplus == 1 ~ "MCI",
    mciamem  == 1 ~ "MCI",
    normcog  == 1 ~ "NL",
    TRUE ~ NA_character_
  ))
```

Generate visit numbers.
```{r}
df_u3_cln_mut <- calculate_visit_num(df_u3_cln_mut,
                                     id = ptid,
                                     date_field = form_date)
```

Find LFDSS items with multiple responses; then filter out.
```{r}
# names(df_u3_cln_mut)[
#   str_detect(string = names(df_u3_cln_mut), pattern = "lfdss_")
#   ]
# names(df_u3_cln_mut)[
#   str_detect(string = names(df_u3_cln_mut), pattern = "worker_")
#   ]

prefilter <- nrow(df_u3_cln_mut)

df_u3_cln_mut <- df_u3_cln_mut %>% 
  rowwise() %>% 
  mutate(lfdss_financial_decision_1_sum = 
           sum(lfdss_financial_decision_1___1,
               lfdss_financial_decision_1___2,
               lfdss_financial_decision_1___3,
               lfdss_financial_decision_1___4,
               lfdss_financial_decision_1___5,
               lfdss_financial_decision_1___6,
               lfdss_financial_decision_1___7,
               lfdss_financial_decision_1___8)) %>% 
  mutate(lfdss_whose_idea_2_sum = 
           sum(lfdss_whose_idea_2___0,
               lfdss_whose_idea_2___1,
               lfdss_whose_idea_2___2)) %>% 
  mutate(lfdss_purpose_3_sum = 
           sum(lfdss_purpose_3___1,
               lfdss_purpose_3___2, 
               lfdss_purpose_3___3,
               lfdss_purpose_3___4,
               lfdss_purpose_3___5,
               lfdss_purpose_3___6)) %>% 
  mutate(lfdss_primary_goal_4_sum = 
           sum(lfdss_primary_goal_4___1,
               lfdss_primary_goal_4___2, 
               lfdss_primary_goal_4___3,
               lfdss_primary_goal_4___4,
               lfdss_primary_goal_4___5,
               lfdss_primary_goal_4___6,
               lfdss_primary_goal_4___7,
               lfdss_primary_goal_4___8, 
               lfdss_primary_goal_4___9,
               lfdss_primary_goal_4___10)) %>% 
  mutate(lfdss_impact_5_sum = 
           sum(lfdss_impact_5___0,
               lfdss_impact_5___1,
               lfdss_impact_5___2,
               lfdss_impact_5___3)) %>% 
  mutate(lfdss_risk_6_sum =
           sum(lfdss_risk_6___0,
               lfdss_risk_6___1,
               lfdss_risk_6___2,
               lfdss_risk_6___3)) %>% 
  mutate(lfdss_neg_affected_7_sum = 
           sum(lfdss_neg_affected_7___0,
               lfdss_neg_affected_7___1,
               lfdss_neg_affected_7___2,
               lfdss_neg_affected_7___3, 
               lfdss_neg_affected_7___4)) %>% 
  mutate(lfdss_who_benefits_8_sum = 
           sum(lfdss_who_benefits_8___1,
               lfdss_who_benefits_8___2,
               lfdss_who_benefits_8___3, 
               lfdss_who_benefits_8___4,
               lfdss_who_benefits_8___5,
               lfdss_who_benefits_8___6,
               lfdss_who_benefits_8___7)) %>% 
  mutate(lfdss_change_plans_9_sum =
           sum(lfdss_change_plans_9___0,
               lfdss_change_plans_9___1,
               lfdss_change_plans_9___2)) %>% 
  mutate(lfdss_talk_to_anyone_10_sum =
           sum(lfdss_talk_to_anyone_10___0,
               lfdss_talk_to_anyone_10___1,
               lfdss_talk_to_anyone_10___2,
               lfdss_talk_to_anyone_10___3)) %>% 
  mutate(worker_1_sum = 
           sum(worker_1___1, 
               worker_1___2, 
               worker_1___3, 
               worker_1___4,
               worker_1___5,
               worker_1___6,
               worker_1___7,
               worker_1___8)) %>% 
  mutate(worker_2_sum = 
           sum(worker_2___0,
               worker_2___1,
               worker_2___2)) %>% 
  mutate(worker_3_sum =
           sum(worker_3___1,
               worker_3___2,
               worker_3___3,
               worker_3___4,
               worker_3___5,
               worker_3___6)) %>% 
  mutate(worker_4_sum =
           sum(worker_4___1,
               worker_4___2,
               worker_4___3,
               worker_4___4,
               worker_4___5,
               worker_4___6,
               worker_4___7,
               worker_4___8,
               worker_4___9,
               worker_4___10)) %>% 
  mutate(worker_5_sum =
           sum(worker_5___0,
               worker_5___1,
               worker_5___2,
               worker_5___3)) %>% 
  mutate(worker_6_sum =
           sum(worker_6___0,
               worker_6___1,
               worker_6___2,
               worker_6___3)) %>% 
  mutate(worker_7_sum =
           sum(worker_7___0,
               worker_7___1,
               worker_7___2,
               worker_7___3,
               worker_7___4)) %>% 
  mutate(worker_8_sum =
           sum(worker_8___1,
               worker_8___2,
               worker_8___3,
               worker_8___4,
               worker_8___5,
               worker_8___6,
               worker_8___7)) %>% 
  mutate(worker_9_sum =
           sum(worker_9___0,
               worker_9___1,
               worker_9___2)) %>% 
  mutate(worker_10_sum =
           sum(worker_10___0,
               worker_10___1,
               worker_10___2,
               worker_10___3)) %>% 
  ungroup() %>%
  filter_at(vars(ends_with("_sum")), all_vars(. <= 1))

postfilter <- nrow(df_u3_cln_mut)
```

(`r prefilter - postfilter` records had multiple responses and so were filtered out.)

Recode LFDSS items (importart are 2, 5, 6, 7, 8, 9, 10) by collapsing dummy variables. Unscored items (1, 3, 4) just get raw values; scored items are recoded to ordinal values. (See "LFDSS scoring for total risk score.pdf".)
```{r}
# names(df_u3_cln_mut)

df_u3_cln_mut <- df_u3_cln_mut %>% 
  mutate(lfdss_financial_decision_1 = case_when(
    lfdss_financial_decision_1___1 == 1 ~ 1,
    lfdss_financial_decision_1___2 == 1 ~ 2,
    lfdss_financial_decision_1___3 == 1 ~ 3,
    lfdss_financial_decision_1___4 == 1 ~ 4,
    lfdss_financial_decision_1___5 == 1 ~ 5,
    lfdss_financial_decision_1___6 == 1 ~ 6,
    lfdss_financial_decision_1___7 == 1 ~ 7,
    lfdss_financial_decision_1___8 == 1 ~ 8,
    TRUE ~ NA_real_
  )) %>% 
  mutate(lfdss_whose_idea_2_ord = case_when(
    lfdss_whose_idea_2___0 == 1 ~ 0,
    lfdss_whose_idea_2___1 == 1 ~ 1,
    lfdss_whose_idea_2___2 == 1 ~ 2,
    TRUE ~ NA_real_)) %>% 
  mutate(lfdss_purpose_3 = case_when(
    lfdss_purpose_3___1 == 1 ~ 1,
    lfdss_purpose_3___2 == 1 ~ 2, 
    lfdss_purpose_3___3 == 1 ~ 3,
    lfdss_purpose_3___4 == 1 ~ 4,
    lfdss_purpose_3___5 == 1 ~ 5,
    lfdss_purpose_3___6 == 1 ~ 6,
    TRUE ~ NA_real_)) %>%
  mutate(lfdss_primary_goal_4 = case_when(
    lfdss_primary_goal_4___1 == 1 ~ 1,
    lfdss_primary_goal_4___2 == 1 ~ 2, 
    lfdss_primary_goal_4___3 == 1 ~ 3,
    lfdss_primary_goal_4___4 == 1 ~ 4,
    lfdss_primary_goal_4___5 == 1 ~ 5,
    lfdss_primary_goal_4___6 == 1 ~ 6,
    lfdss_primary_goal_4___7 == 1 ~ 7,
    lfdss_primary_goal_4___8 == 1 ~ 8,
    lfdss_primary_goal_4___9 == 1 ~ 9,
    lfdss_primary_goal_4___10 == 1 ~ 10,
    TRUE ~ NA_real_)) %>% 
  mutate(lfdss_impact_5_ord = case_when(
    lfdss_impact_5___0 == 1 ~ 0,
    lfdss_impact_5___1 == 1 ~ 1,
    lfdss_impact_5___2 == 1 ~ 2,
    lfdss_impact_5___3 == 1 ~ 3,
    TRUE ~ NA_real_)) %>% 
  mutate(lfdss_risk_6_ord = case_when(
    lfdss_risk_6___0 == 1 ~ 0,
    lfdss_risk_6___1 == 1 ~ 1,
    lfdss_risk_6___2 == 1 ~ 2,
    lfdss_risk_6___3 == 1 ~ 3,
    TRUE ~ NA_real_)) %>% 
  mutate(lfdss_neg_affected_7_ord = case_when(
    lfdss_neg_affected_7___0 == 1 ~ 0,
    lfdss_neg_affected_7___1 == 1 ~ 1,
    lfdss_neg_affected_7___2 == 1 ~ 1,
    lfdss_neg_affected_7___3 == 1 ~ 1, 
    lfdss_neg_affected_7___4 == 1 ~ 2,
    TRUE ~ NA_real_)) %>% 
  mutate(lfdss_who_benefits_8_ord = case_when(
    lfdss_who_benefits_8___1 == 1 ~ 0,
    lfdss_who_benefits_8___2 == 1 ~ 1,
    lfdss_who_benefits_8___3 == 1 ~ 1,
    lfdss_who_benefits_8___4 == 1 ~ 1,
    lfdss_who_benefits_8___5 == 1 ~ 1,
    lfdss_who_benefits_8___6 == 1 ~ 1,
    lfdss_who_benefits_8___7 == 1 ~ 2,
    TRUE ~ NA_real_)) %>% 
  mutate(lfdss_change_plans_9_ord = case_when(
    lfdss_change_plans_9___0 == 1 ~ 0,
    lfdss_change_plans_9___1 == 1 ~ 1,
    lfdss_change_plans_9___2 == 1 ~ 2,
    TRUE ~ NA_real_)) %>% 
  mutate(lfdss_talk_to_anyone_10_ord = case_when(
    lfdss_talk_to_anyone_10___0 == 1 ~ 0,
    lfdss_talk_to_anyone_10___1 == 1 ~ 0,
    lfdss_talk_to_anyone_10___2 == 1 ~ 0,
    lfdss_talk_to_anyone_10___3 == 1 ~ 1,
    TRUE ~ NA_real_)) %>% 
  mutate(worker_1 = case_when(
    worker_1___1 == 1 ~ 1, 
    worker_1___2 == 1 ~ 2,
    worker_1___3 == 1 ~ 3,
    worker_1___4 == 1 ~ 4,
    worker_1___5 == 1 ~ 5,
    worker_1___6 == 1 ~ 6,
    worker_1___7 == 1 ~ 7,
    worker_1___8 == 1 ~ 8,
    TRUE ~ NA_real_)) %>% 
  mutate(worker_2_ord = case_when(
    worker_2___0 == 1 ~ 0,
    worker_2___1 == 1 ~ 1,
    worker_2___2 == 1 ~ 2)) %>% 
  mutate(worker_3 = case_when(
    worker_3___1 == 1 ~ 1,
    worker_3___2 == 1 ~ 2,
    worker_3___3 == 1 ~ 3,
    worker_3___4 == 1 ~ 4,
    worker_3___5 == 1 ~ 5,
    worker_3___6 == 1 ~ 6,
    TRUE ~ NA_real_)) %>% 
  mutate(worker_4 = case_when(
    worker_4___1 == 1 ~ 1,
    worker_4___2 == 1 ~ 2,
    worker_4___3 == 1 ~ 3,
    worker_4___4 == 1 ~ 4,
    worker_4___5 == 1 ~ 5,
    worker_4___6 == 1 ~ 6,
    worker_4___7 == 1 ~ 7,
    worker_4___8 == 1 ~ 8,
    worker_4___9 == 1 ~ 9,
    worker_4___10 == 1 ~ 10,
    TRUE ~ NA_real_)) %>% 
  mutate(worker_5_ord = case_when(
    worker_5___0 == 1 ~ 0,
    worker_5___1 == 1 ~ 1,
    worker_5___2 == 1 ~ 2,
    worker_5___3 == 1 ~ 3,
    TRUE ~ NA_real_)) %>% 
  mutate(worker_6_ord = case_when(
    worker_6___0 == 1 ~ 0,
    worker_6___1 == 1 ~ 1,
    worker_6___2 == 1 ~ 2,
    worker_6___3 == 1 ~ 3,
    TRUE ~ NA_real_)) %>% 
  mutate(worker_7_ord = case_when(
    worker_7___0 == 1 ~ 0,
    worker_7___1 == 1 ~ 1,
    worker_7___2 == 1 ~ 1,
    worker_7___3 == 1 ~ 1,
    worker_7___4 == 1 ~ 2,
    TRUE ~ NA_real_)) %>% 
  mutate(worker_8_ord = case_when(
    worker_8___1 == 1 ~ 0,
    worker_8___2 == 1 ~ 1,
    worker_8___3 == 1 ~ 1,
    worker_8___4 == 1 ~ 1,
    worker_8___5 == 1 ~ 1,
    worker_8___6 == 1 ~ 1,
    worker_8___7 == 1 ~ 2,
    TRUE ~ NA_real_)) %>% 
  mutate(worker_9_ord = case_when(
    worker_9___0 == 1 ~ 0,
    worker_9___1 == 1 ~ 1,
    worker_9___2 == 1 ~ 2,
    TRUE ~ NA_real_)) %>% 
  mutate(worker_10_ord = case_when(
    worker_10___0 == 1 ~ 0,
    worker_10___1 == 1 ~ 0,
    worker_10___2 == 1 ~ 0,
    worker_10___3 == 1 ~ 1,
    TRUE ~ NA_real_))
```

Collapse `lfdss_dec_abil_score` dummy variables.
```{r}
# names(df_u3_cln_mut)[
#   str_detect(names(df_u3_cln_mut), pattern = "lfdss_dec_abil_score")
#   ]

df_u3_cln_mut <- df_u3_cln_mut %>% 
  mutate(lfdss_dec_abil_score = case_when(
    lfdss_dec_abil_score___1 == 1 ~ 1,
    lfdss_dec_abil_score___2 == 1 ~ 2,
    lfdss_dec_abil_score___3 == 1 ~ 3,
    TRUE ~ NA_real_
  ))
```

Check for discrepances between "client" and "worker" items.
```{r}
df_u3_cln_mut <- df_u3_cln_mut %>%
  mutate(lfdss_2_agree = case_when(
    lfdss_whose_idea_2_ord == worker_2_ord ~ 1L,
    lfdss_whose_idea_2_ord != worker_2_ord ~ 0L,
    TRUE ~ NA_integer_
  )) %>% 
  mutate(lfdss_5_agree = case_when(
    lfdss_impact_5_ord == worker_5_ord ~ 1L,
    lfdss_impact_5_ord != worker_5_ord ~ 0L,
    TRUE ~ NA_integer_
  )) %>% 
  mutate(lfdss_6_agree = case_when(
    lfdss_risk_6_ord == worker_6_ord ~ 1L,
    lfdss_risk_6_ord != worker_6_ord ~ 0L,
    TRUE ~ NA_integer_
  )) %>% 
  mutate(lfdss_7_agree = case_when(
    lfdss_neg_affected_7_ord == worker_7_ord ~ 1L,
    lfdss_neg_affected_7_ord != worker_7_ord ~ 0L,
    TRUE ~ NA_integer_
  )) %>% 
  mutate(lfdss_8_agree = case_when(
    lfdss_who_benefits_8_ord == worker_8_ord ~ 1L,
    lfdss_who_benefits_8_ord != worker_8_ord ~ 0L,
    TRUE ~ NA_integer_
  )) %>% 
  mutate(lfdss_9_agree = case_when(
    lfdss_change_plans_9_ord == worker_9_ord ~ 1L,
    lfdss_change_plans_9_ord != worker_9_ord ~ 0L,
    TRUE ~ NA_integer_
  )) %>% 
  mutate(lfdss_10_agree = case_when(
    lfdss_talk_to_anyone_10_ord == worker_10_ord ~ 1L,
    lfdss_talk_to_anyone_10_ord != worker_10_ord ~ 0L,
    TRUE ~ NA_integer_
  ))
```

Resolve "client"-"worker" discrepances. If there's a discrepancy between the client and worker ordinal scores, the get raised to the "don't know" category with a maximum ordinal score.
```{r}
df_u3_cln_mut <- df_u3_cln_mut %>%
  mutate(lfdss_whose_idea_2_ord_res = case_when(
    lfdss_2_agree == 0 ~ 2,
    TRUE ~ lfdss_whose_idea_2_ord
  )) %>% 
  mutate(lfdss_impact_5_ord_res = case_when(
    lfdss_5_agree == 0 ~ 3,
    TRUE ~ lfdss_impact_5_ord
  )) %>% 
  mutate(lfdss_risk_6_ord_res = case_when(
    lfdss_6_agree == 0 ~ 3,
    TRUE ~ lfdss_risk_6_ord
  )) %>% 
  mutate(lfdss_neg_affected_7_ord_res = case_when(
    lfdss_7_agree == 0 ~ 2,
    TRUE ~ lfdss_neg_affected_7_ord
  )) %>% 
  mutate(lfdss_who_benefits_8_ord_res = case_when(
    lfdss_8_agree == 0 ~ 2,
    TRUE ~ lfdss_who_benefits_8_ord
  )) %>% 
  mutate(lfdss_change_plans_9_ord_res = case_when(
    lfdss_9_agree == 0 ~ 2,
    TRUE ~ lfdss_change_plans_9_ord
  )) %>% 
  mutate(lfdss_talk_to_anyone_10_ord_res = case_when(
    lfdss_10_agree == 0 ~ 1,
    TRUE ~ lfdss_talk_to_anyone_10_ord
  ))
```

Add summation field for all client-worker resolved ordinal scores.
```{r}
df_u3_cln_mut <- df_u3_cln_mut %>% 
  rowwise() %>% 
  mutate(lfdss_ord_res_sum = 
           sum(lfdss_whose_idea_2_ord_res,
               lfdss_impact_5_ord_res,
               lfdss_risk_6_ord_res,
               lfdss_neg_affected_7_ord_res,
               lfdss_who_benefits_8_ord_res,
               lfdss_change_plans_9_ord_res,
               lfdss_talk_to_anyone_10_ord_res)) %>% 
  ungroup()
```

Add summation field for _Lichtenberg Financial Decision Self Efficacy_ fields.
```{r}
df_u3_cln_mut <- df_u3_cln_mut %>%
  rowwise() %>% 
  mutate(lfdrs_self_eff_sum =
           sum(lfdrs_sa_6_confident,
               lfdrs_sa7_worry,
               lfdrs_pv_21_anxious,
               lfdrs_pv_24_downhearted)) %>% 
  ungroup()
```


#### MiNDSet Registry

Coerce data types.
```{r}
# purrr::map(df_ms_cln, class)
df_ms_cln_mut <- df_ms_cln %>% 
  mutate(race_value = as.integer(race_value),
         sex_value  = as.integer(sex_value),
         ed_level   = as.integer(ed_level),
         marital_status = as.integer(marital_status),
         exam_date  = as.Date(exam_date),
         birth_date = as.Date(birth_date))
# purrr::map(df_ms_cln_mut, class)
```

Add age.
```{r}
df_ms_cln_mut <- calculate_age(df_ms_cln_mut,
                               birth_date = birth_date,
                               age_date = exam_date)
```

### Filter data

#### UDS 3

Get only most recent visits.
```{r}
df_u3_cln_mut_flt <- get_visit_n(df_u3_cln_mut,
                                 id_field = ptid,
                                 date_field = form_date,
                                 n = Inf) # -Inf => earliest visit
                                          # Inf  => most recent visit
```

Keep only records that have worker data.
```{r}
df_u3_cln_mut_flt <- df_u3_cln_mut_flt %>% 
  filter(!is.na(worker_2_ord))
```


## Join Data

### Left join: UDS 3 + MiNDSet Registry

Get rid of `redcap_event_name` fields.
```{r}
df_u3_cln_mut_flt <- df_u3_cln_mut_flt %>% 
  select(-redcap_event_name)
df_ms_cln_mut <- df_ms_cln_mut %>% 
  select(-redcap_event_name)
```

Perform left outer join.
```{r}
df_u3_ms <-
  FuzzyDateJoin::outer_left(x = df_u3_cln_mut_flt,    y = df_ms_cln_mut,
                            x_id_col = "ptid",        y_id_col = "subject_id",
                            x_date_col = "form_date", y_date_col = "exam_date",
                            x_intvl_less = 120L, x_intvl_more = 120L,
                            keep_y_id = FALSE)
```

Reorder fields.
```{r}
# names(df_u3_ms)
df_u3_ms <- df_u3_ms %>%
  dplyr::select(
    -birth_date,
    -normcog, 
    -mciamem, -mciaplus,
    -mcinon1, -mcinon2,
    -impnomci,
    -alzdis, -alzdisif,
    -lbdis, -lbdif,
    -msa, -msaif,
    -psp, -pspif,
    -ftldmo, -ftldmoif,
    -ftldnos, -ftldnoif
  ) %>% 
  dplyr::select(ptid, form_date, visit_num, 
                uds_dx_der, uds_dx_date = exam_date,
                age_years, age_exact, age_units,
                race_value, sex_value, ed_level, marital_status,
                mocatots, trailb_c2, trailbrr_c2, trailbli_c2, trailb_c2z,
                lfdrs_sa_6_confident, lfdrs_sa7_worry, 
                lfdrs_pv_21_anxious, lfdrs_pv_24_downhearted,
                lfdrs_self_eff_sum, 
                everything())
```


## Write Data

```{r}
readr::write_csv(df_u3_ms, "df_u3_ms.csv", na = "")
```


## Build Data Dictionaries

### UDS 3
```{r}
names_df_u3_ms <- names(df_u3_ms)
names_df_u3_ms <- str_replace_all(names_df_u3_ms, "___\\d{1,2}$", "")

json_data_dict_u3 <- RCurl::postForm(
  uri          = REDCAP_API_URI,
  token        = REDCAP_API_TOKEN_UDS3n,
  content      = 'metadata',
  format       = 'json',
  returnFormat = 'json'
)
df_data_dict_u3 <- jsonlite::fromJSON(json_data_dict_u3)

df_data_dict_u3_flt <- df_data_dict_u3 %>% 
  filter(field_name %in% names_df_u3_ms)
```

### MiNDSet Registry
```{r}
# names_df_u3_ms <- names(df_u3_ms)

json_data_dict_ms <- RCurl::postForm(
  uri          = REDCAP_API_URI,
  token        = REDCAP_API_TOKEN_MINDSET,
  content      = 'metadata',
  format       = 'json',
  returnFormat = 'json'
)
df_data_dict_ms <- jsonlite::fromJSON(json_data_dict_ms)

df_data_dict_ms_flt <- df_data_dict_ms %>% 
  filter(field_name %in% names_df_u3_ms)
```

## Write Data Dictionaries

```{r}
readr::write_csv(df_data_dict_u3_flt, "DataDictionary_UDS3.csv", na = "")
readr::write_csv(df_data_dict_ms_flt, "DataDictionary_MiNDSet.csv", na = "")
```


## Find Records Missing LFDSS Worker Data

```{r}
# df_u3_ms %>% 
#   select(ptid, form_date, worker_2_ord) %>% 
#   filter(form_date >= as.Date("2018-03-01")) %>% 
#   filter(is.na(worker_2_ord)) %>%
#   select(-worker_2_ord) %>% 
#   arrange(ptid, form_date) %>% 
#   readr::write_csv("missing_lfdss_worker_data.csv", na = "")
```




